Figures

### 2019-05-09 figures/07_model-selection.Rmd
explore multivariate focal predictors

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "hu12_ppt_mean", 
                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
                "soybeans", "pasture", 
                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, 
                           !is.na(phosphorusvfertilizervuse), 
                           !is.na(soybeans), 
                           !is.na(maxdepth), 
                           !is.na(tp))
dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))

@@

# linear re with multivariate focal predictor
model_form <- bf(tp ~ maxdepth + iwslavratio + (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit2.rds")
fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form, 
                         data = dt)
# plot(fit1)
# print(fit$formula)

loo_compare(loo(fit1), loo(fit2))

>>>>

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                "tp", "hu12_ppt_mean", "hu12_baseflow_mean",
                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
                "soybeans", "pasture", 
                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, 
                           !is.na(phosphorusvfertilizervuse), 
                           !is.na(soybeans), 
                           !is.na(corn),
                           !is.na(maxdepth), 
                           !is.na(tp))
dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))

@@

model_form <- bf(tp ~ hu12vbaseflowvmean + 
                   (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit2.rds")
fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form, 
                         data = dt)

# linear re with multivariate focal predictor
model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
                   (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit3.rds")
fit3 <- get_if_not_exists(brm_fit, "../data/mcmc/fit3.rds", formula = model_form, 
                         data = dt)

model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
                   (1 + soybeans | hu4vzoneid))
# unlink("../data/mcmc/fit4.rds")
fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
                         data = dt)

loo_compare(loo(fit3), loo(fit4))

model_form <- bf(tp ~ maxdepth + iwslavratio + 
                   (1 + corn | hu4vzoneid))
# unlink("../data/mcmc/fit3.rds")
fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
                         data = dt)

brms::bayes_R2(fit2)
brms::bayes_R2(fit3)
brms::bayes_R2(fit4)
